The Quantum Sneakernet

### 2019-01-22 Simon's section/main.tex
Added bib, figs, edits

The development of a model for the quantum internet \cite{?} has a distinct advantage over all other communication networks that have preceded it, namely the ability to leverage a treasure trove of information about how global communications systems are used, their inefficiencies, choke-points and vulnerabilities. The knowledge we have gained provides a unique design opportunity in the quantum realm, namely, 
\\
\\
\textit{If we had the ability to redesign an entirely new internet from scratch, how would we go about it? What would we do differently?}
\\
\\
The hardware required to transmit quantum information around the globe will coexist in parallel with the classical internet, since at the very least a fast classical network is required to communicate the classical information necessary to complete many quantum information processing protocols, such as quantum state teleportation or entanglement swapping. At a minimum, we can conclude that a global quantum network will be \textit{rate limited}\index{Rate limiting} by the classical network supporting it. However, given that the classical internet presently has the capacity to transmit information at approximately 70\% of the speed of light (in standard silica fibre optics), over global distances, at extremely high data-rates, means we will have to be industrious in establishing large-scale quantum networks before the classical side-channel produces significant bottlenecks.\comment{Don't get this last part of the sentence}

There have traditionally been three major candidates for distributing quantum information over long-distance communications channel:
\begin{itemize}
\item Optic fibre transmission and quantum repeaters \cite{?}.
\item Direct free-space transmission \cite{?}.
\item Quantum satellites \cite{?}. 
\end{itemize}

All of these techniques employ photons as the carrier of quantum information and have already been deployed in QKD protocols \cite{?}. However, there are several issues with these techniques that could make building a global quantum network challenging.

While QKD remains the foremost protocol deployed on current quantum communication hardware, a true global quantum internet must handle a vast array of potential applications, including linking fully error-corrected quantum computing systems \cite{?}. Consequently, we need to consider several metrics in potential hardware implementations. Four primary metrics can be identified:
\begin{itemize}
\item Speed: How many qubits can be transmitted per second?
\item Distance: How far can we transmit qubits, while maintaining the requird speed?
\item Fidelity: How accurately can each qubit be transmitted, while maintaining the required speed and distance?
\item Cost: What is the monetary cost of building, deploying and maintaining the hardware underlying a quantum channel of given speed, distance, and fidelity?
\end{itemize}

@@

In this chapter we discuss some of the practical demands that must be taken into account when constructing a quantum internet (in the context of QKD), and introduce a fourth type of model for global quantum networking, the quantum Sneakernet. We will take a qualitative look at its structure and operation, and argue that there are many potential practical and economic merits to employing it as the backbone technology in a global network.

@@

A 2016 assessment from the UK's cyber intelligence agency GCHQ\index{GCHQ} cites four concerns with QKD as an effective replacement for classical techniques:
\begin{itemize}
\item \textit{QKD protocols only address key exchange}: Ubiquitous on-demand modern services (such as verifying identities and data integrity, establishing network sessions, providing access control, and automatic software updates) rely more on authentication and integrity mechanisms such as digital signatures than on encryption.
\item \textit{Commercial QKD systems operate over relatively short distances, and BB84 (and other similar protocols) are inherently point-to-point protocols}: This means that QKD does not integrate easily with the classical internet, or with widespread mobile technologies, apps, and services.
\item \textit{Hardware is relatively expensive to purchase and maintain}: Unlike software, hardware cannot be patched remotely or cheaply when it degrades or vulnerabilities are discovered.
\item \textit{Real-world QKD systems are built from classical components (e.g sources, detectors, fibres, and ancillary classical network devices), any of which may prove a point of failure}: A number of attacks have been proposed and demonstrated on deployed QKD systems that subvert hardware components, enabling the recovery of secret keys without detection.
\item \textit{Denial-of-service (DoS) attacks\index{Denial-of-service (DoS) attacks} that disrupt transmissions are potentially easier with QKD than with classical internet or mobile network technologies}: Since QKD devices typically abort a key establishment session upon detecting tampering, it is difficult to recommend QKD in situations where DoS attacks are likely.
\end{itemize}

@@

Before detailing the specifics of a Sneakernet-based entanglement distribution network, let us first discuss the general framework the system leverages in the context of QKD. This is the principle of physically-trusted couriers and one-time-pads. The general technique, utilised routinely for extremely sensitive applications, does not transmit key material over any classical network, instead entrusting a physical courier with pre-loaded key material on a portable memory stick.

@@

The key technology underpinning a quantum Sneakernet is the fabrication and packaging of long-lived \textit{active} quantum memories. Quantum memories are inherently fragile, owing to the extreme susceptibility of quantum information to decoherence induced by environmental interactions. Today's best physical qubits typically have lifetimes on the order of $\sim$1ms. While there has been significant research into finding or engineering quantum systems with lifetimes on the order of seconds or minutes, these systems are notoriously hard to control (i.e information read-in/out is challenging), because they have been purposefully engineered to be so isolated from the environment that control signals are effectively isolated too. The ability to build useful quantum technology requires increasing effective quantum memory times (e.g $T_1$- and $T_2$-times\index{T$_1$-times}\index{T$_2$-times}), such that they can be utilised over timescales appropriate for human manipulation.

The problem of increasing effective lifetimes was solved with the formulation of active QEC protocols, where a single \textit{logical} qubit\index{Logical qubits} is encoded into a finite number of \textit{physical} qubits\index{Physical qubits}. Continuous operations on the array of physical qubits extract information about physical errors, and, provided physical error rates are sufficiently low, the logically encoded information can be preserved over arbitrary timescales. Unlike specially engineered quantum systems that are isolated to achieve long lifetimes, encoded memories consist of intrinsically unstable physical qubits. However, encoded information in the system is maintained for arbitrary timescales via the active QEC. Active quantum memories form the foundational building blocks of a quantum Sneakernet network, allowing us to maintain encoded quantum information for extremely long durations (potentially even decades), sufficient for most important real-world applications.

@@

Considering the major, well-developed qubit technologies, we summarise their relative advantages and disadvantages. In many systems, \textit{infrastructure requirements} appear to be the most significant barrier to portability. These major technologies are:
\begin{itemize}
\item \textbf{Superconducting qubits}\index{Superconducting qubits}: require operational temperatures of $\sim$30mK to maintain operational coherence. Such temperatures require dilution refrigeration\index{Dilulion refrigeration}, which is clumsy and undermines portability. 
\item \textbf{Ion traps}\index{Ion traps}: require an almost perfect vacuum environment, which again may prove to be implementationally problematic. 
\item \textbf{Linear optics}\index{Linear optics}: avoids issues such as vacuums and extremely low temperatures, but gate non-determinism introduces impractical physical overheads. 
\item \textbf{Quantum dots}\index{Quantum dots}: similar to superconducting technology, dilution refrigeration is required.
\item \textbf{Phosphorus in Silicon}\index{Phosphorus in Silicon}: Also requires dilution refrigeration. 
\item \textbf{Colour centres (e.g. NV-diamond)}\index{Colour centres}\index{NV-diamond}: Neither vacuums nor dilution refrigeration are required. 
\end{itemize}

Colour centres, at least from the context of building large, portable qubit arrays, appear most promising candidate. In colour centres, a single atomic defect is inserted into a crystal substrate. For example, a Nitrogen defect in a perfect diamond crystal of Carbon, providing a so-called \textit{spin vacuum substrate}\index{Spin vacuum substrates}. Essentially, the crystal surrounding the defect provides the same isolation properties that an actual physical vacuum does in other technologies. Additionally, many colour centres operate at temperatures of only $\sim$4K. While still cold, 4K cryogenic technology is far simpler than the dilution refrigeration systems required to achieve a 30mK thermal environment. 4K cryogenic technology is so advanced that we are able to effectively launch them into space. Thirdly, colour centres are generally \textit{optically accessible}\index{Optical accessibility}. An optically accessible colour centre has, in general, an electronic transition in the donor system that is resonant at optical frequencies. This allows for remote coupling of colour centres using optical photons, which are comparatively easy to route in and out of the crystal and surrounding 4K infrastructure. This is in contrast to superconducting qubits, which interact with microwave photons that are difficult to route, or systems such as Phosphorus in Silicon that generally utilise direct dipole/dipole or exchange-based coupling to realise gates.

@@

Active quantum error-corrected devices are the cornerstone of scalable quantum computation and communication. There has been significant discussion surrounding so-called Noisy Intermediate-Scale Quantum (NISQ) applications\index{Noisy Intermediate-Scale Quantum (NISQ) technology}. That is, applications small enough to not require QEC. However, no NISQ application has yet been identified of scientific or commercial relevance that can be performed without employing resource-costly QEC protocols. QKD is a case in point. One of the major implementation-related drawbacks of current QKD technology arises from the physical errors that occur during qubit transmission, and the limited ranges and rates induced by them.

@@

Surface code\index{Surface codes} QEC is a well-known technique for active QEC, that is being developed by several of the major hardware vendors in quantum computation. The basic idea is that a square 2D array of interacting qubits is needed to encode a \textit{logical} piece of quantum information to extend its natural lifetime beyond the individual \textit{physical} lifetimes of the constituent physical qubits. The basic schematic is shown in Fig.~\ref{fig:array}.

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{array}
	\caption{} \label{fig:array}
\end{figure}

@@

The surface code has been extremely well studied over the past 15 years. We have extremely accurate simulations that detail the threshold behaviour of the code under a variety of different assumptions and we have quantified very well how the scaling of the code behaves as a function of physical error rate. For this reason we are able to quantify expected \textit{logical} memory time, $T$, in terms of the physical operation time of the quantum gates in our hardware, $t$, the number of physical qubits in the QMU array, $N$, and the logical error rate we want to target, $P$. Through direct numerical simulation, we find,
\begin{align} \label{eq:scale}
T \approx 10t\sqrt{N} P(70p)^{-\sqrt{N}/4},
\end{align}
where $p$ is the physical error rate associated with each of the qubits within each QMU -- assumed to be at least below the fault-tolerant threshold of the planar code, $p_\mathrm{th} \approx 0.7\%$.

@@

The point where logical information within the QMU can be reliably stored for longer than approximately 1 seconds is the boundary of what we define as \textit{macroscopic quantum memories}. A macroscopic quantum memory is something that can store information long enough to start physically transporting the QMU. Clearly the longer you can reliably store the information in the QMU the further it can be physically moved, but a memory of at least 1 second is needed before you can start doing something interesting using Sneakernet principles.

It should be emphasised that the estimates in Fig.~\ref{fig:array} are based on QEC techniques that are unoptimised for a specific hardware chipset. Performing error correction decoding on a system with biased noise can change resource overheads and it is possible for other QEC coding techniques to be invented that is compatible with hardware engineering constraints that scales better than Eq.~(\ref{eq:scale}) for the rotated planar code. This could reduce the required physical qubit array sizes for a given QMU memory. However, the key message here is that a physical qubit array of on the order of 1cm$^2$, with physical gate times of order 1$\mu$s can be made into very long-lived quantum memories using the same architectural structures and assumptions of quantum computing systems that are already under development (we just require the added property of portability).

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{goal}
	\caption{} \label{fig:goal}
\end{figure}

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{cost}
	\caption{} \label{fig:price}.
\end{figure}

@@

This issue of PPQ is of critical concern for large-scale quantum computing systems. Shown in Fig.~\ref{fig:price} are costing out of a quantum computing system of sufficient size to perform Shor's factoring algorithm for large key sizes and for quantum simulation of nitrogenase\index{Nitrogenase} molecules for nitrogen fixation. If an ultimate PPQ goal is not \$1 or lower, there may be little economic motivation for building more than a handful of quantum computers globally. It should be noted that PPQ needs to take into account the infrastructure and control systems as well as the physical qubit itself. For example, in superconducting systems, the required dilution refrigeration system is expensive -- around \$500,000. Additionally, the sample chamber for the dilution refrigerator is quite small in comparison to the `footprint' of a superconducting qubit. A commercial dilution refrigeration system can accommodate perhaps 100 such physical qubits. Consequently, at a minimum, the PPQ in this system would be \$5,000. Additionally Fig.~\ref{fig:price} does not include any R\&D expenditure or the costs associated with building the fabrication infrastructure to build the qubits themselves.

@@

The basic operational primitive of the quantum Sneakernet system is an old technique for the long range distribution of information. As encapsulated in this wonderful quote from the former director of the University of Toronto Computing Services (UTCS):
\\
\\
\famousquote{Never underestimate the bandwidth of a station wagon full of tapes hurtling down the highway.}{Warren Jackson}
\\
\\
While essentially everyone today is familiar with the principle of classical Sneakernets, many people are not familiar with the name. Rather than sending information via radio waves or fibre optic cables, information it's loaded onto storage memory and physically transported from source to destination. The viability of Sneakernets in the classical world depends heavily on three practical considerations:
\begin{itemize}
\item Availability of cheap, high capacity classical memories
\item Limited bandwidth and high costs associated with radio or optical fibre communications channels
\item The need or lack of need for low latency communications 
\end{itemize}

The first practical consideration for Sneakernet communications has been solved. Classical memories have fallen in price and increased in capacity to an even greater degree than transistor price and density. In 2018, Toshiba released a single 3.5-inch hard disk drive with a capacity of 14TB available for \$550 USD.

Let's contrast this capacity with fibre optic connections. In 2016 the new FASTER\index{FASTER} fibre optic communications link was brought online between northern California and Japan. Costing \$300m to deploy, it has a total data capacity of 7.5TB/s across the Pacific. Consequently, it takes two seconds, utilising the full design capacity of a \$300m dollar piece of telecommunications infrastructure, to transmit the data contained on a \$550 device that could fit into a handbag. This \$550 hard drive can be shipped via FedEx from northern California to Tokyo for about an extra \$150 and arrive about twenty hours later. Using that approach, we could achieve the same bandwidth as the FASTER network utilising approximately 36,000 hard drives shipped continuously back and forth. The total cost of this would be approximately \$20m dollars for the hard-drives and \$5m per day in commercial shipping costs (which could be made significantly cheaper by using more dedicated cargo transportation systems than FedEx, which is arguably the most expensive).

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{classical}
	\caption{} \label{fig:classical}
\end{figure}

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{qustick1}
	\caption{} \label{fig:qustick1}
\end{figure}

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{qustick2}
	\caption{} \label{fig:loading}
\end{figure}

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{qustick3}
	\caption{} \label{fig:distribution}
\end{figure}

@@

Another extremely beneficial aspect to the quantum Sneakernet design is the ability to perform entanglement swapping. What does this mean?

@@

Entanglement is a consumable resource. But, unlike a battery, the entanglement `charge' is a free resource that comes as a consequence of two QuSTICKS being in the same room.

>>>>

The development of a model for the quantum internet \cite{SD-Wehner:2018aa} has a distinct advantage over all other communication networks that have preceded it, namely the ability to leverage a treasure trove of information about how global communications systems are used, their inefficiencies, choke-points and vulnerabilities. The knowledge we have gained provides a unique design opportunity in the quantum realm, namely, 
\\
\\
\textit{If we had the ability to redesign an entirely new internet from scratch, how would we go about it? What would we do differently?}
\\
\\
The hardware required to transmit quantum information around the globe will coexist in parallel with the classical internet, since at the very least a fast classical network is required to communicate the classical information necessary to complete many quantum information processing protocols, such as quantum state teleportation or entanglement swapping. At a minimum, we can conclude that a global quantum network will be \textit{rate limited}\index{Rate limiting} by the classical network supporting it. However, given that the classical internet presently has the capacity to transmit information at approximately 70\% of the speed of light (in standard silica fibre optics), over global distances, at extremely high data-rates, means we will have to be industrious in establishing large-scale quantum networks before the classical side-channel becomes a potential rate-limiting factor of the quantum communications protocols themselves\footnote{We are referring here to the classical component of a quantum protocol such as teleportation or key exchange, not bottlenecks that may be encountered in {\em establishing} quantum entanglement through a technology such as repeaters because of a high amount of back-and-forth classical information exchange in the repeater network}.

There have traditionally been three major candidates for distributing quantum information over long-distance communications channel:
\begin{itemize}
\item Optic fibre transmission and quantum repeaters \cite{SD-Fowler:2010aa,SD-Sangouard:2011aa,SD-Munro:2012aa,SD-Azuma:2015aa}.
\item Direct free-space transmission \cite{SD-Ursin:2007aa,SD-Ma:2012aa}.
\item Quantum satellites \cite{SD-Tang:2016aa,SD-Takenaka:2017aa,SD-Yin:2017aa}. 
\end{itemize}

All of these techniques employ photons as the carrier of quantum information and have already been deployed in QKD protocols \cite{SD-Schmitt-Manderbach:2007aa,SD-Peev:2009aa,SD-Liao:2017aa}. However, there are several issues with these techniques that could make building a global quantum network challenging.

While QKD remains the foremost protocol deployed on current quantum communication hardware, a true global quantum internet must handle a vast array of potential applications, including linking fully error-corrected quantum computing systems \cite{SD-Devitt2011,SD-Fitzsimons:2017aa}. Consequently, we need to consider several metrics in potential hardware implementations. Four primary metrics can be identified:
\begin{itemize}
\item Speed: How many qubits can be transmitted per second?
\item Distance: How far can we transmit qubits, while maintaining the required speed?
\item Fidelity: How accurately can each qubit be transmitted, while maintaining the required speed and distance?
\item Cost: What is the monetary cost of building, deploying and maintaining the hardware underlying a quantum channel of given speed, distance, and fidelity?
\end{itemize}

@@

In this chapter we discuss some of the practical demands that must be taken into account when constructing a quantum internet (in the context of QKD), and introduce a fourth type of model for global quantum networking, the quantum Sneakernet \cite{SD-Devitt:2016aa}. We will take a qualitative look at its structure and operation, and argue that there are many potential practical and economic merits to employing it as the backbone technology in a global network.

@@

A 2016 assessment from the UK's cyber intelligence agency GCHQ\index{GCHQ} cites four concerns with QKD as an effective replacement for classical techniques \href{https://www.ncsc.gov.uk/whitepaper/quantum-key-distribution}{https://www.ncsc.gov.uk/whitepaper/quantum-key-distribution}:
\begin{itemize}
\item \textit{QKD protocols only address key exchange}: Ubiquitous on-demand modern services (such as verifying identities and data integrity, establishing network sessions, providing access control, and automatic software updates) rely more on authentication and integrity mechanisms such as digital signatures than on encryption.
\item \textit{Commercial QKD systems operate over relatively short distances, and BB84 (and other similar protocols) are inherently point-to-point protocols}: This means that QKD does not integrate easily with the classical internet, or with widespread mobile technologies, apps, and services.
\item \textit{Hardware is relatively expensive to purchase and maintain}: Unlike software, hardware cannot be patched remotely or cheaply when it degrades or vulnerabilities are discovered.
\item \textit{Real-world QKD systems are built from classical components (e.g sources, detectors, fibres, and ancillary classical network devices), any of which may prove a point of failure}: A number of attacks have been proposed and demonstrated on deployed QKD systems that subvert hardware components, enabling the recovery of secret keys without detection.
\item \textit{Denial-of-service (DoS) attacks\index{Denial-of-service (DoS) attacks} that disrupt transmissions are potentially easier with QKD than with classical internet or mobile network technologies}: Since QKD devices typically abort a key establishment session upon detecting tampering, it is difficult to recommend QKD in situations where DoS attacks are likely.
\end{itemize}

@@

Before detailing the specifics of a Sneakernet-based entanglement distribution network, let us first discuss the general framework the system leverages in the context of QKD. This is the principle of physically-trusted couriers \cite{SD-Merkle:1978:SCO:359460.359473} and one-time-pads \cite{SD-Shannon:1949aa}. The general technique, utilised routinely for extremely sensitive applications, does not transmit key material over any classical network, instead entrusting a physical courier with pre-loaded key material on a portable memory stick.

@@

The key technology underpinning a quantum Sneakernet is the fabrication and packaging of long-lived \textit{active} quantum memories \cite{SD-Terhal:2015aa}. Quantum memories are inherently fragile, owing to the extreme susceptibility of quantum information to decoherence induced by environmental interactions. Today's best physical qubits typically have lifetimes on the order of $\sim$1ms-1s. While there has been significant research into finding or engineering quantum systems with lifetimes on the order of minutes or hours \cite{SD-Zhong:2015aa,SD-Rancic:2017aa,SD-Astner:2018aa}, these systems are notoriously hard to control (i.e information read-in/out is challenging), because they have been purposefully engineered to be so isolated from the environment that control signals are effectively isolated too. The ability to build useful quantum technology requires increasing effective quantum memory times (e.g $T_1$- and $T_2$-times\index{T$_1$-times}\index{T$_2$-times}), such that they can be utilised over timescales appropriate for human manipulation.

The problem of increasing effective lifetimes was solved with the formulation of active QEC protocols \cite{SD-Devitt:2013aa}, where a single \textit{logical} qubit\index{Logical qubits} is encoded into a finite number of \textit{physical} qubits\index{Physical qubits}. Continuous operations on the array of physical qubits extract information about physical errors, and, provided physical error rates are sufficiently low, the logically encoded information can be preserved over arbitrary timescales. Unlike specially engineered quantum systems that are isolated to achieve long lifetimes, encoded memories consist of intrinsically unstable physical qubits. However, encoded information in the system is maintained for arbitrary timescales via the active QEC. Active quantum memories form the foundational building blocks of a quantum Sneakernet network, allowing us to maintain encoded quantum information for extremely long durations (potentially even decades), sufficient for most important real-world applications.

@@

Considering the major, well-developed qubit technologies, we summarise their relative advantages and disadvantages. In many systems, \textit{infrastructure requirements} appear to be the most significant barrier to portability. These major technologies are:
\begin{itemize}
\item \textbf{Superconducting qubits}\index{Superconducting qubits}: require operational temperatures of $\sim$30mK to maintain operational coherence. Such temperatures require dilution refrigeration\index{Dilulion refrigeration}, which is clumsy and undermines portability. 
\item \textbf{Ion traps}\index{Ion traps}: require an almost perfect vacuum environment, which again may prove to be implementationally problematic. 
\item \textbf{Linear optics}\index{Linear optics}: avoids issues such as vacuums and extremely low temperatures, but gate non-determinism introduces -- currently -- impractical physical overheads. 
\item \textbf{Quantum dots}\index{Quantum dots}: similar to superconducting technology, dilution refrigeration is required.
\item \textbf{Phosphorus in Silicon}\index{Phosphorus in Silicon}: Also requires dilution refrigeration. 
\item \textbf{Colour centres (e.g. NV-diamond)}\index{Colour centres}\index{NV-diamond}: Neither vacuums nor dilution refrigeration are required. 
\end{itemize}

Colour centres, at least from the context of building large, portable qubit arrays, appear most promising candidate. In colour centres, a single atomic defect is inserted into a crystal substrate. For example, a Nitrogen defect in a perfect diamond crystal of Carbon, providing a so-called \textit{spin vacuum substrate}\index{Spin vacuum substrates} \cite{SD-Aharonovich:2011aa}. Essentially, the crystal surrounding the defect provides the same isolation properties that an actual physical vacuum does in other technologies. Additionally, many colour centres operate at temperatures of only $\sim$4K. While still cold, 4K cryogenic technology is far simpler than the dilution refrigeration systems required to achieve a 30mK thermal environment. 4K cryogenic technology is so advanced that we are able to effectively launch them into space \cite{SD-Gehrz2007}. Thirdly, colour centres are generally \textit{optically accessible}\index{Optical accessibility}. An optically accessible colour centre has, in general, an electronic transition in the donor system that is resonant at optical frequencies. This allows for remote coupling of colour centres using optical photons, which are comparatively easy to route in and out of the crystal and surrounding 4K infrastructure. This is in contrast to superconducting qubits, which interact with microwave photons that are difficult to route \cite{SD-Kurpiers:2018aa}, or systems such as Phosphorus in Silicon that generally utilise direct dipole/dipole or exchange-based coupling to realise gates \cite{SD-Tosi:2017aa}.

@@

Active quantum error-corrected devices are the cornerstone of scalable quantum computation and communication. There has been significant discussion surrounding so-called Noisy Intermediate-Scale Quantum (NISQ) applications\index{Noisy Intermediate-Scale Quantum (NISQ) technology} \cite{SD-Preskill2018quantumcomputingin}. That is, applications small enough to not necessarily require QEC. However, no NISQ application has yet been identified of scientific or commercial relevance that can be performed without employing resource-costly QEC protocols. QKD is a case in point. One of the major implementation-related drawbacks of current QKD technology arises from the physical errors that occur during qubit transmission, and the limited ranges and rates induced by them.

@@

Surface code\index{Surface codes} QEC is a well-known technique for active QEC, that is being developed by several of the major hardware vendors in quantum computation \cite{SD-Fowler:2012aa}. The basic idea is that a square 2D array of interacting qubits is needed to encode a \textit{logical} piece of quantum information to extend its natural lifetime beyond the individual \textit{physical} lifetimes of the constituent physical qubits. The basic schematic is shown in Fig.~\ref{fig:array}.

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{array}
	\caption{Expected resource overhead for a Quantum Memory Unit based on rotated planar codes \cite{SD-Horsman:2012aa}.  A 2D nearest neighbour array of physical qubits can be used to encode a single {\em logical qubit} of quantum information.  Provided the underlying hardware has a physical error rate associated with initialisation, measurement, single and two-qubit gates less than the fault-tolerant threshold of the surface code -- approximately 0.7\% --  increasing the size of the lattice will exponentially increase the effective coherence time of the stored information.  In the table we illustrate an example of a QMU built from a physical array of qubits that have a physical separation of 250$\mu$m, physical gate times of $t=1\mu$s and physical error rates of $p=0.1\%$.  We specify the expected {\em logical} memory time at a {\em logical} fidelity of 99.99\% for a hardware with stochastic, balanced qubit noise \cite{SD-Devitt:2016aa}.} 
	\label{fig:array}
\end{figure}

@@

The surface code has been extremely well studied over the past 15 years. We have extremely accurate simulations that detail the threshold behaviour of the code under a variety of different assumptions and we have quantified very well how the scaling of the code behaves as a function of physical error rate \cite{SD-Stace:2010aa,SD-Wang:2011aa,SD-Stephens:2014aa,SD-Nagayama:2017aa,SD-Tuckett:2018aa}. For this reason we are able to quantify expected \textit{logical} memory time, $T$, in terms of the physical operation time of the quantum gates in our hardware, $t$, the number of physical qubits in the QMU array, $N$, and the logical error rate we want to target, $P$. Through direct numerical simulation, we find \cite{SD-Devitt:2016aa},
\begin{align} \label{eq:scale}
T \approx 10t\sqrt{N} P(70p)^{-\sqrt{N}/4},
\end{align}
where $p$ is the physical error rate associated with each of the qubits within each QMU -- assumed to be at least below the fault-tolerant threshold of the planar code, $p_\mathrm{th} \approx 0.7\%$ \cite{SD-Fowler:2012aa}.

@@

The point where logical information within the QMU can be reliably stored for longer than approximately 1 seconds is the boundary of what we define as \textit{macroscopic quantum memories}. A macroscopic quantum memory is something that can store information long enough to start physically moving the QMU. Clearly the longer you can reliably store the information in the QMU the further it can be physically moved, but a memory of at least 1 second is needed before you can start doing something interesting using Sneakernet principles.

It should be emphasised that the estimates in Fig.~\ref{fig:array} are based on QEC techniques that are unoptimised for a specific hardware chipset. Performing error correction decoding on a system with biased noise \cite{SD-Tuckett:2018aa} can change resource overheads and it is possible for other QEC coding techniques to be invented that is compatible with hardware engineering constraints that scales better than Eq.~(\ref{eq:scale}) for the rotated planar code \cite{SD-Bombin:2015aa,SD-Breuckmann:2017aa,SD-Fawzi:2018aa}. This could reduce the required physical qubit array sizes for a given QMU memory. However, the key message here is that a physical qubit array of on the order of 1cm$^2$, with physical gate times of order 1$\mu$s can be made into very long-lived quantum memories using the same architectural structures and assumptions of quantum computing systems that are already under development (we just require the added property of portability) \cite{SD-Jones:2012aa,SD-Gimeno-Segovia:2015aa,SD-Nemoto:2014aa,SD-Hill:2015aa,SD-Lekitsch:2017aa}.

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{goal}
	\caption{Key properties of the underlying physical hardware technology that allows for quantum Sneakernet operations.} \label{fig:goal}
\end{figure}

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{cost}
	\caption{Exponential decrease of the cost of classical transistors over the past 50 years.  Plot was constructed using data from \cite{SD-Berndt2000,} } \label{fig:price}.
\end{figure}

@@

This issue of PPQ is of critical concern for large-scale quantum computing systems. Shown in Fig.~\ref{fig:price} are costing out of a quantum computing system of sufficient size to perform Shor's factoring algorithm for large key sizes and for quantum simulation of nitrogenase\index{Nitrogenase} molecules for nitrogen fixation \cite{SD-Fowler:2012aa,SD-Reiher:2017aa}. If an ultimate PPQ goal is not \$1 or lower, there may be little economic motivation for building more than a handful of quantum computers globally. It should be noted that PPQ needs to take into account the infrastructure and control systems as well as the physical qubit itself. For example, in superconducting systems, the required dilution refrigeration system is expensive -- around \$500,000. Additionally, the sample chamber for the dilution refrigerator is quite small in comparison to the `footprint' of a superconducting qubit. A commercial dilution refrigeration system can accommodate perhaps 100 such physical qubits. Consequently, at a minimum, the PPQ in this system would be \$5,000. Additionally Fig.~\ref{fig:price} does not include any R\&D expenditure or the costs associated with building the fabrication infrastructure to build the qubits themselves.

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{PPQ}
	\caption{Examples of resource estimates for Shor's algorithm \cite{SD-Fowler:2012aa} and quantum chemistry simulations for Nitrogen fixation \cite{SD-Reiher:2017aa}.  Large numbers of physical qubits are needed for a fully error-corrected implementation.  If the price per qubit for the actual hardware is not at least close to the \$1 mark, the price of the machine may outweigh any economic benefit to the calculation.  These costs do not include R\&D or infrastructure costs associated with the computers development.} \label{fig:price}.
\end{figure}

@@

The basic operational primitive of the quantum Sneakernet system is an old technique for the long range distribution of information. As encapsulated in this wonderful quote from the former director of the University of Toronto Computing Services (UTCS):
\\
\\
\famousquote{Never underestimate the bandwidth of a station wagon full of tapes hurtling down the highway.}{Warren Jackson}
\\
\\
While essentially everyone today is familiar with the principle of classical Sneakernets, many people are not familiar with the name \href{https://en.wikipedia.org/wiki/Sneakernet}{https://en.wikipedia.org/wiki/Sneakernet}. Rather than sending information via radio waves or fibre optic cables, information it's loaded onto storage memory and physically transported from source to destination. The viability of Sneakernets in the classical world depends heavily on three practical considerations:
\begin{itemize}
\item Availability of cheap, high capacity classical memories
\item Limited bandwidth and high costs associated with radio or optical fibre communications channels
\item The need or lack of need for low latency communications 
\end{itemize}

The first practical consideration for Sneakernet communications has been solved. Classical memories have fallen in price and increased in capacity to an even greater degree than transistor price and density. In 2018, Toshiba released a single 3.5-inch hard disk drive with a capacity of 14TB available for \$550 USD \href{https://www.amazon.com/Toshiba-14TB-SATA-7200RPM-Enterprise/dp/B07DHY61JP}{https://www.amazon.com/Toshiba-14TB-SATA-7200RPM-Enterprise/dp/B07DHY61JP}.

Let's contrast this capacity with fibre optic connections. In 2016 the new FASTER\index{FASTER} fibre optic communications link was brought online between northern California and Japan. Costing \$300m to deploy, it has a total data capacity of 7.5Tbps/s across the Pacific \href{https://www.nec.com/en/press/201408/global_20140811_01.html}{https://www.nec.com/en/press/201408/global_20140811_01.html}. Consequently, it takes two seconds, utilising the full design capacity of a \$300m dollar piece of telecommunications infrastructure, to transmit the data contained on a \$550 device that could fit into a handbag. This \$550 hard drive can be shipped via FedEx from northern California to Tokyo for about an extra \$150 and arrive about twenty hours later -- based on advertised prices from FedEx for door-to-door express shipping of a 1kg unit. Using that approach, we could achieve the same bandwidth as the FASTER network utilising approximately 36,000 hard drives shipped continuously back and forth. The total cost of this would be approximately \$20m dollars for the hard-drives and \$5m per day in commercial shipping costs (which could be made significantly cheaper by using more dedicated cargo transportation systems than FedEx, which is arguably the most expensive).

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{classical}
	\caption{Satellite information from the Union of Concerned Scientists Satellite datebase \href{https://www.ucsusa.org/nuclear-weapons/space-weapons/satellite-database?_ga=2.192846958.535241894.1547878264-1715284942.1547878264#.XEK_gi1L1ro}{https://www.ucsusa.org/nuclear-weapons/space-weapons/satellite-database?_ga=2.192846958.535241894.1547878264-1715284942.1547878264#.XEK_gi1L1ro}.  Submarine optic cable data from wikipedia \href{https://en.wikipedia.org/wiki/List_of_international_submarine_communications_cables}{https://en.wikipedia.org/wiki/List_of_international_submarine_communications_cables}.  Global internet traffic sourced from \href{https://www.statista.com/statistics/499431/global-ip-data-traffic-forecast/}{https://www.statista.com/statistics/499431/global-ip-data-traffic-forecast/}.} \label{fig:classical}
\end{figure}

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{qustick1}
	\caption{A QuSTICK is a portable device containing a collection of active QMU's.  The QuSTICK is to be portable and ideally with an optical interface to the physical qubits comprising each QMU.  In the case of colour centers, which in general have optical transitions available, interacting physical qubits within QMU's and between QMU's separated by a small amount of optic fibre should be nearly identical.  Hence two separate QuSTICK units can be coupled together, entangling respective QMU's in each unit into Bell states.} \label{fig:qustick1}
\end{figure}

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{qustick2}
	\caption{QuSTICK units can be manufactured and entangled locally.  Due to the portability of the units, they can be physically shipped.  This distributes the entanglement directly, without transmitting quantum information via free space or optic fibre over long distances.  The internal error correction of each QMU will maintain the coherence of the entangled states during the physical transport.} \label{fig:loading}
\end{figure}

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{qustick3}
	\caption{Entangled QMU units can be distributed anywhere that conventional shipping transport can go.  A distributed, high-fidelity quantum network over global distances can be established by simply putting subsets of QuSTICK units onto different transports and moving them to separate locations.} \label{fig:distribution}
\end{figure}

@@

Another extremely beneficial aspect to the quantum Sneakernet design is the ability to perform entanglement swapping \cite{SD-Zukowski:1993aa}. What does this mean?

@@

Entanglement is a consumable resource, and may ultimately end up a marketable commodity in a future {\em entanglement based economy} \cite{SD-Devitt:2016aa}. But, unlike a battery, the entanglement `charge' is a free resource that comes as a consequence of two QuSTICKS being in the same room.
